RDF Constraint Types to Ensure High Data Quality

### 2015-04-28 paper/paper7/paper7.tex
feedback

\begin{document}
\renewcommand{\arraystretch}{1.3}
%
%
%\title{RDF Validation of Metadata \\ on Person-Level and Aggregated Data}
%\title{RDF Constraints to Ensure High Quality \\ of Metadata and Data Represented by any Vocabulary }
%\title{RDF Constraints to Ensure High Quality \\ of Metadata and Data}
\title{Classification of RDF Constraint Types to Ensure High Quality of Metadata and Data}
\subtitle{}

@@

\begin{abstract}
\tb{nur data und nicht metadata}
For research institutes, data libraries, and data archives,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world.
%The data most often used in research within the community around research data for the social, behavioural, and economic sciences (\emph{SBE}) is person-level data, i.e., data collected about individuals (households, businesses). 
%%The DDI-RDF Discovery Vocabulary is used to describe and to discover this kind of research data.
%While performing research, the detailed, often access restricted person-level
%data is aggregated into less confidential publicly available multi-dimensional tables which answer particular research questions and whose purpose is to gain an interest in further more detailed analyses on the underlying person-level data.
To ensure high quality and trust, both metadata and data must satisfy certain criteria - specified in terms of RDF constraints. 
%From 2012 to 2015 together with other Linked Data community members and \emph{SBE} experts, we developed diverse vocabularies to represent \emph{SBE} metadata and data in RDF.

@@

In this paper, we formulate 213 constraints of 53 different types on four different vocabularies (Disco, QB, SKOS, PHDD) and classify them according to the complexity level of their type and their severity level for the vocabulary. Further, for 114 of these constraints, we evaluate the data quality of 15,694 datasets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.

@@

@@

\begin{table}[H]
		\scriptsize
    \begin{center}
    \begin{tabular}{@{}lcccc@{}}
%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
%    \\  \cmidrule{2-7}
    \\       \textbf{Criteria}
           & \textbf{\emph{Disco}}
           & \textbf{\emph{QB}}
					 & \textbf{\emph{SKOS}}
					 & \textbf{Total}
    \\ \midrule
		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
		%\hline
		\emph{C} & 143 (67.1\%) & 35 (16.4\%) & 35 (16.4\%) & 213 \\
		\hline
		\emph{C (}$\mathcal{CT}_{C}$\emph{)} & 37 (25.9\%) & 13 (37.1\%) & 13 (\textbf{37.1\%}) & 63 (29.6\%) \\
		\emph{C (}$\mathcal{CT}_{S}$\emph{)} & 28 (19.6\%) & 3 (8.6\%) & 12 (\textbf{34.3\%}) & 43 (20.2\%) \\
		\emph{C (}$\mathcal{CT}_{B}$\emph{)} & 78 (\textbf{54.6\%}) & 19 (\textbf{54.3\%}) & 10 (\textbf{28.6\%}) & 107 (\textbf{50.2\%}) \\
		\hline
		\emph{C (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 67 (46.9\%) & 13 (37.1\%) & 4 (11.4\%) & 84 (39.4\%) \\
		\emph{C (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 11 (7.7\%) & 6 (17.1\%) & 6 (17.1\%) & 23 (10.8\%) \\
		\hline
		\emph{C ($\mathcal{SL}_{0}$)} & 75 (\textbf{52.5\%}) & 4 (11.4\%) & 21 (\textbf{60\%}) & 100 (\textbf{46.9\%}) \\
		\emph{C ($\mathcal{SL}_{1}$)} & 10 (7\%) & 3 (8.6\%) & 5 (14.3\%) & 18 (8.5\%) \\
		\emph{C ($\mathcal{SL}_{2}$)} & 58 (40.6\%) & 28 (\textbf{80\%}) & 9 (25.7\%) & 95 (\textbf{44.6\%}) \\
    \bottomrule
    \end{tabular}
    %\\ \emph{C (constraints), CT (constraint types)}
    \caption{Evaluation - Constraints}
		\label{tab:evaluation-constraints}
    \end{center}
\end{table}

@@

\begin{table}[H]
		\scriptsize
    \begin{center}
    \begin{tabular}{@{}lcccc@{}}
%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
%    \\  \cmidrule{2-7}
    \\       \textbf{Criteria}
           & \textbf{\emph{Disco}}
           & \textbf{\emph{QB}}
					 & \textbf{\emph{SKOS}}
					 & \textbf{Total}
    \\ \midrule
		\emph{CV} & 3,575,002 (6.5\%) & 45,635,861 (83.4\%) & 5,540,988 (10.1\%) & 54,751,851 \\
		\hline
		\emph{CV (}$\mathcal{CT}_{C}$\emph{)} & 652,780 (18.3\%) & 45,634,084 (\textbf{100\%}) & 1,185,982 (21.4\%) & 47,472,846 (\textbf{86.7\%}) \\
		\emph{CV (}$\mathcal{CT}_{S}$\emph{)} & 560,857 (15.7\%) & 0 (0\%) & 4,355,006 (\textbf{78.6\%}) & 4,915,863 (9\%) \\
		\emph{CV (}$\mathcal{CT}_{B}$\emph{)} & 2,361,365 (\textbf{66.1\%}) & 1,777 (0\%) & 0 (0\%) & 2,363,142 (4.3\%) \\
		\hline
		\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
		\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
		\hline
		\emph{CV ($\mathcal{SL}_{0}$)} & 1,880,777 (\textbf{52.6\%}) & 0 (0\%) & 2,281,740 (41.2\%) & 4,162,517 (7.6\%) \\
		\emph{CV ($\mathcal{SL}_{1}$)} & 1,051,757 (29.4\%) & 45,520,613 (\textbf{99,8\%}) & 3,259,248 (\textbf{58.8\%}) & 49,831,618 (\textbf{91\%}) \\
		\emph{CV ($\mathcal{SL}_{2}$)} & 642,468 (18\%) & 115,248 (0.3\%) & 0 (0\%) & 757,716 (1.4\%) \\
    \bottomrule
    \end{tabular}
    %\\ \emph{CV (constraint violations)}
    \caption{Evaluation - Constraint Violations}
		\label{tab:evaluation-constraint-violations}
    \end{center}
\end{table}

More than 80\% of the overall approx. 55 million constraint violations are caused by \emph{QB} constraints (see table \ref{tab:evaluation-constraint-violations}).
The majority (86.7\%) of the constraint violations are caused by $\mathcal{CT}_{C}$ constraints and only 9\% by $\mathcal{CT}_{S}$ constraints.
The fact that only 4\% of all constraint violations result from $\mathcal{CT}_{B}$ constraints, 
even though, more than 50\% of all constraints are $\mathcal{CT}_{B}$ constraints,
is an indicator that data producers achieve good data quality with respect to the constraints extracted by vocabularies.
Two-thirds of the constraint violations, thrown for \emph{Disco} data sets, result from $\mathcal{CT}_{B}$ constraints,
almost only $\mathcal{CT}_{C}$ constraints raised constraint violations for \emph{QB} data sets, and 
nearly 80\% of the \emph{SKOS} constraint violations are caused by $\mathcal{CT}_{S}$ constraints.
Although, only 8.5\% of all constraints are $\mathcal{SL}_{1}$ constraints,
9 0f 10 constraint violations are caused by constraints associated with the default severity level $\mathcal{SL}_{1}$.
More than 50\% of all constraint violations thrown for \emph{Disco} data sets are not seen to be that significant ($\mathcal{SL}_{0}$).
Almost all constraint violations raised by \emph{QB} constraints and 59\% of the constraint violations caused by \emph{SKOS} constraints are classified as warnings ($\mathcal{SL}_{1}$).  
As this evaluation serves as indication for \emph{good} or \emph{bad} (meta)data quality, 
we conclude that
the metadata quality of all evaluated \emph{Disco} data sets is \emph{good} and that the metadata quality of all evaluated \emph{QB} and \emph{SKOS} data sets is \emph{satisfactory}.
%The constraints responsible for the largest amounts of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916; \emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102; \emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903; \emph{SKOS}).

>>>>

\begin{document}
\renewcommand{\arraystretch}{1.3}
%
%
%\title{RDF Validation of Metadata \\ on Person-Level and Aggregated Data}
%\title{RDF Constraints to Ensure High Quality \\ of Metadata and Data Represented by any Vocabulary }
%\title{RDF Constraints to Ensure High Quality \\ of Metadata and Data}
\title{RDF Constraint Types to Ensure High Data Quality}
\subtitle{}

@@

\begin{abstract}

For research institutes, data libraries, and data archives,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world.
%The data most often used in research within the community around research data for the social, behavioural, and economic sciences (\emph{SBE}) is person-level data, i.e., data collected about individuals (households, businesses). 
%%The DDI-RDF Discovery Vocabulary is used to describe and to discover this kind of research data.
%While performing research, the detailed, often access restricted person-level
%data is aggregated into less confidential publicly available multi-dimensional tables which answer particular research questions and whose purpose is to gain an interest in further more detailed analyses on the underlying person-level data.
To ensure high quality and trust, both metadata and data must satisfy certain criteria - specified in terms of RDF constraints. 
%From 2012 to 2015 together with other Linked Data community members and \emph{SBE} experts, we developed diverse vocabularies to represent \emph{SBE} metadata and data in RDF.

@@

In this paper, we formulate 213 constraints of 53 different types on four different vocabularies (Disco, QB, SKOS, PHDD) and classify them according to the complexity level of their type and their severity level. For 114 of these constraints, we evaluate the data quality of 15,694 datasets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.

@@

\tb{nur data und nicht metadata}

@@

\begin{table}[H]
		\scriptsize
    \begin{center}
    \begin{tabular}{@{}lcccc@{}}
%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
%    \\  \cmidrule{2-7}
    \\       \textbf{Criteria}
           & \textbf{\emph{Disco}}
           & \textbf{\emph{QB}}
					 & \textbf{\emph{SKOS}}
					 & \textbf{Total}
    \\ \midrule
		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
		%\hline
		\emph{C} & 143 (67.1\%) & 35 (16.4\%) & 35 (16.4\%) & 213 \\
		\hline
		\emph{C (}$\mathcal{CT}_{C}$\emph{)} & 37 (25.9\%) & 13 (37.1\%) & 13 (\textbf{37.1\%}) & 63 (29.6\%) \\
		\emph{C (}$\mathcal{CT}_{S}$\emph{)} & 28 (19.6\%) & 3 (8.6\%) & 12 (\textbf{34.3\%}) & 43 (20.2\%) \\
		\emph{C (}$\mathcal{CT}_{B}$\emph{)} & 78 (\textbf{54.6\%}) & 19 (\textbf{54.3\%}) & 10 (\textbf{28.6\%}) & 107 (\textbf{50.2\%}) \\
		%\hline
		%\emph{C (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 67 (46.9\%) & 13 (37.1\%) & 4 (11.4\%) & 84 (39.4\%) \\
		%\emph{C (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 11 (7.7\%) & 6 (17.1\%) & 6 (17.1\%) & 23 (10.8\%) \\
		\hline
		\emph{C ($\mathcal{SL}_{0}$)} & 75 (\textbf{52.5\%}) & 4 (11.4\%) & 21 (\textbf{60\%}) & 100 (\textbf{46.9\%}) \\
		\emph{C ($\mathcal{SL}_{1}$)} & 10 (7\%) & 3 (8.6\%) & 5 (14.3\%) & 18 (8.5\%) \\
		\emph{C ($\mathcal{SL}_{2}$)} & 58 (40.6\%) & 28 (\textbf{80\%}) & 9 (25.7\%) & 95 (\textbf{44.6\%}) \\
    \bottomrule
    \end{tabular}
    %\\ \emph{C (constraints), CT (constraint types)}
    \caption{Evaluation - Constraints}
		\label{tab:evaluation-constraints}
    \end{center}
\end{table}

@@

\begin{table}[H]
		\scriptsize
    \begin{center}
    \begin{tabular}{@{}lcccc@{}}
%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
%    \\  \cmidrule{2-7}
    \\       \textbf{Criteria}
           & \textbf{\emph{Disco}}
           & \textbf{\emph{QB}}
					 & \textbf{\emph{SKOS}}
					 & \textbf{Total}
    \\ \midrule
		\emph{CV} & 3,575,002 & 45,635,861 & 5,540,988 & 54,751,851 \\
		\hline
		\emph{CV (}$\mathcal{CT}_{C}$\emph{)} & 18.3\% & 45,634,084 (\textbf{100\%}) & 1,185,982 (21.4\%) & 47,472,846 (\textbf{86.7\%}) \\
		\emph{CV (}$\mathcal{CT}_{S}$\emph{)} & 15.7\% & 0 (0\%) & 4,355,006 (\textbf{78.6\%}) & 4,915,863 (9\%) \\
		\emph{CV (}$\mathcal{CT}_{B}$\emph{)} & \textbf{66.1\%} & 1,777 (0\%) & 0 (0\%) & 2,363,142 (4.3\%) \\
		%\hline
		%\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
		%\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
		\hline
		\emph{CV ($\mathcal{SL}_{0}$)} & 1,880,777 (\textbf{52.6\%}) & 0 (0\%) & 2,281,740 (41.2\%) & 4,162,517 (7.6\%) \\
		\emph{CV ($\mathcal{SL}_{1}$)} & 1,051,757 (29.4\%) & 45,520,613 (\textbf{99,8\%}) & 3,259,248 (\textbf{58.8\%}) & 49,831,618 (\textbf{91\%}) \\
		\emph{CV ($\mathcal{SL}_{2}$)} & 642,468 (18\%) & 115,248 (0.3\%) & 0 (0\%) & 757,716 (1.4\%) \\
    \bottomrule
    \end{tabular}
    %\\ \emph{CV (constraint violations)}
    \caption{Evaluation - Constraint Violations}
		\label{tab:evaluation-constraint-violations}
    \end{center}
\end{table}
\tb{prozent beziehen sich auf die oberste zeile / auch 0.0\%}
\textcolor{red}{wir versuchen eine aussage zu trefen für alle vokabulare mit werten nur von 3 vokabularen / vorsichtig generelle aussagen zu treffen / normalisiterte werte mit prozentwerten / neues vokabulare, noch nicht so konsistente daten / hypothesen werden aufgestellt / conclusion: hypothesen werden aufgestellt, die vorsichtig zu genießen sind / basic constraints sind bei etablierten vokabularen publitierte datensätze werden eingehalten hohe datenqualität / schwerwiegende constraintverletzungen treten kaum auf / schwere constraints sind in idesen vielen daten nicht auf / disco ist in beiden fällen anders / erheblichen anteil von schwersten constraint verletzungen / disco neues vokabular das noch daten gelten noch einenm draft von disco oder hat disco nicht verstanden schnlechtere daten als entabliete vokabulare / es ist sinnvoll sprachen zu entwickeln komplexere constraints auszudrücken / simple und vocabulary können heute schon sehr gut beschrieben werden / wir wünschen und dass es komplexere constraint languages gibt mit denen complex constraints besser abgebildet werden können / deulticherer verbesserung in der datenualitt wenn wir diese constraint languages hätten / gibt es weitere hypothesen? - alles was in der tabelle auffällig ist / normaliisert über die datensatzgröße / 3 sehr wichtige und repräsentative vokabulare im sbe bereich / interessanate constraints mit ausreißern / hypothesen über weitere vokabulare müssen verifiziert oder falsifiziert werden / diskussion: / 3 constraints werden zufällig nie verletzt / basis für future work / motivation, dass man constraint languages entwicken muss die complexe constraints abbilden / datenqualität ist generell sehr hoch / als hypothese postulieren}
More than 80\% of the overall approx. 55 million constraint violations are caused by \emph{QB} constraints (see table \ref{tab:evaluation-constraint-violations}).
The majority (86.7\%) of the constraint violations are caused by $\mathcal{CT}_{C}$ constraints and only 9\% by $\mathcal{CT}_{S}$ constraints.
The fact that only 4\% of all constraint violations result from $\mathcal{CT}_{B}$ constraints, 
even though, more than 50\% of all constraints are $\mathcal{CT}_{B}$ constraints,
is an indicator that data producers achieve good data quality with respect to the constraints extracted by vocabularies.
Two-thirds of the constraint violations, thrown for \emph{Disco} data sets, result from $\mathcal{CT}_{B}$ constraints,
almost only $\mathcal{CT}_{C}$ constraints raised constraint violations for \emph{QB} data sets, and 
nearly 80\% of the \emph{SKOS} constraint violations are caused by $\mathcal{CT}_{S}$ constraints.
Although, only 8.5\% of all constraints are $\mathcal{SL}_{1}$ constraints,
9 0f 10 constraint violations are caused by constraints associated with the default severity level $\mathcal{SL}_{1}$.
More than 50\% of all constraint violations thrown for \emph{Disco} data sets are not seen to be that significant ($\mathcal{SL}_{0}$).
Almost all constraint violations raised by \emph{QB} constraints and 59\% of the constraint violations caused by \emph{SKOS} constraints are classified as warnings ($\mathcal{SL}_{1}$).  
As this evaluation serves as indication for \emph{good} or \emph{bad} (meta)data quality, 
we conclude that
the metadata quality of all evaluated \emph{Disco} data sets is \emph{good} and that the metadata quality of all evaluated \emph{QB} and \emph{SKOS} data sets is \emph{satisfactory}.
%The constraints responsible for the largest amounts of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916; \emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102; \emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903; \emph{SKOS}).
